CrypTool Script \\ Mathematics and Cryptography

### 2002-09-06 script/de/chapters/numbertheory.tex
no message

Dieser Rekord, aufgestellt am 18. Januar 2002 von Forschern der Universit"at Bonn, fand deutlich 
weniger Aufmerksamkeit in der Presse als die L"osung der RSA-Challenge vom 22. Oktober 1999, als niederl"andische
Forscher eine 155-stellige Zahl in ihre beiden 78-stellige Primfaktoren zerlegten (vergleiche Kapitel \ref{chptSecurityParam}).

>>>>

Dieser Rekord, aufgestellt am 18. Januar 2002 von Forschern der Universit"at Bonn \linebreak[4]
\href{http://www.uni-bonn.de/Aktuelles/Pressemitteilungen/pm02/pm035-02.html}
{\texttt{http://www.uni-bonn.de/Aktuelles/Pressemitteilungen/pm02/pm035-02.html}}, fand deutlich 
weniger Aufmerksamkeit in der Presse als die L"osung der RSA-Challenge vom 22. Oktober 1999, als niederl"andische
Forscher eine 155-stellige Zahl in ihre beiden 78-stellige Primfaktoren zerlegten (vergleiche Kapitel \ref{chptSecurityParam}).

### 2002-09-06 script/en/chapters/numbertheory.tex
no message

This record, established on January 18, 2002 by researchers of the German
university of Bonn, got much less attention within the press than the
solution of the RSA challenge, established on August 22, 1999, when
researchers from the Netherlands factorized the 155-digit number into its
both 78-digit primes (see Chapter \ref{chptSecurityParam}).

>>>>

This record, established on January 18, 2002 by researchers of the German
university of Bonn (see the press statement (in german language): \\
\href{http://www.uni-bonn.de/Aktuelles/Pressemitteilungen/pm02/pm035-02.html}
{\texttt{http://www.uni-bonn.de/Aktuelles/Pressemitteilungen/pm02/pm035-02.html}}), got much less attention within the press than the
solution of the RSA challenge, established on August 22, 1999, when
researchers from the Netherlands factorized the 155-digit number into its
both 78-digit primes (see Chapter \ref{chptSecurityParam}).
